---
title: 'Assignment: R Markdown Presentation & Plotly'
author: Eric Henderson
date: June 9th, 2017
output: ioslides_presentation
---


```{r, message=FALSE, echo=FALSE}
# load libraries
library(plotly)

#load data
theData <- read.csv(file="simplemaps-worldcities-basic.csv")
theData <- theData[order(-theData$pop),]
```

## Assignment Details

Guidelines:

- Create a R Markdown presentation

- Display a plot with Plotly

Implementation:

The next slide shows a Plotly plot of Latitude vs Longitude of city data from http://simplemaps.com/data/world-cities. While not particularly informative, it is an interesting way to visualize the data and to find that the plotting of 7,332 cities location data roughly draws the outlines of the continents.

## City Data (Lattitude vs Longitude)

```{r, echo=FALSE}
plot_ly(data = theData, x = ~lng, y = ~lat, type = "scatter", mode = "markers")
```

## The R Markdown Code to Display Plot

```{r, message=FALSE, echo=TRUE, eval=FALSE}
# load libraries
library(plotly)

#load data
theData <- read.csv(file="simplemaps-worldcities-basic.csv")
theData <- theData[order(-theData$pop),]

plot_ly(data = theData, x = ~lng, y = ~lat,
        type = "scatter", mode = "markers")
```